### 2023-06-03 python_excel_ite.tex
working on nb 1

@@

% Private macros here (check that there is no clash with the style)

@@

@@

What kind of Python background do students need have in order to be ready for this EwP module? This module does presume a basic familiarity with Python fundamentals for data analysis such as:

@@

>>>>

\usepackage{hyperref}
\usepackage{listings}
\usepackage{xcolor}

@@

% Private macros here (check that there is no clash with the style)
\definecolor{LightGray}{gray}{0.9}
\definecolor{codegreen}{rgb}{0,0.6,0}
\definecolor{codegray}{rgb}{0.5,0.5,0.5}
\definecolor{codepurple}{rgb}{0.58,0,0.82}
\definecolor{backcolour}{rgb}{0.95,0.95,0.92}
\lstdefinestyle{mystyle}{
	backgroundcolor=\color{LightGray},   
    commentstyle=\color{codegreen},
	keywordstyle=\color{magenta},
	numberstyle=\tiny\color{codegreen},
	stringstyle=\color{codepurple},
	basicstyle=\footnotesize\ttfamily,
	breakatwhitespace=false,         
	breaklines=true,                 
	captionpos=b,                    
	keepspaces=true,                 
	numbers=left,                    
	numbersep=5pt,                  
	showspaces=false,                
	showstringspaces=false,
	showtabs=false,                  
	tabsize=2
}

\lstset{style=mystyle}

@@

- more topics I wanted to cover than were possible in PCDA course
- weave in more SE type material which is often overlooked in BA programs

@@

PCDA ends with intro to sklearn and AAP begins with review of sklearn and some more ML content - logistic regression with regularization

What kind of Python background do students need to have in order to be ready for this EwP module? This module does presume a basic familiarity with Python fundamentals for data analysis such as:

@@

This example is based on one in the [spreadsheet modeling textbook(s) I've used in my classes since 2001](https://host.kelley.iu.edu/albrightbooks/). I started out using Practical Management Science by Winston and Albright and switched to their Business Analytics: Data Analysis and Decision Making (Albright and Winston) around 2013ish. In both books, they introduce the "Walton Bookstore" problem in the chapter on Monte-Carlo simulation. Here's the basic problem (with a few modifications):

\begin{itemize}
	\item we have to place an order for a perishable product (e.g. a calendar),
	\item there's a known unit cost for each one ordered,
	\item we have a known selling price,
	\item demand is uncertain but we can model it with some simple probability distribution,
	\item for each unsold item, we can get a partial refund of our unit cost,
	\item we need to select the order quantity for our one order for the year; orders can only be in multiples of 25.
\end{itemize}

The notebook begins with a suggestion to start with a very simple model that ignores the demand uncertainty and that is not object oriented. Proceeding much like we would in Excel, we store base input values in variables. (unit cost, unit price, selling prce, unit refund and demand)

\begin{lstlisting}[language=Python]
order_cost = unit_cost * order_quantity
sales_revenue = ??? * selling_price
refund_revenue = ??? * unit_refund
profit = sales_revenue + refund_revenue - order_cost
\end{lstlisting}
